My title

### 2024-04-17 paper/paper.qmd
Few changes

# Read in all the data
data_2009 <- read_csv("~/Final paper/data/raw_data/raw_data_2009.csv")
data_2010 <- read_csv("~/Final paper/data/raw_data/raw_data_2010.csv")
data_2011 <- read_csv("~/Final paper/data/raw_data/raw_data_2011.csv")
data_2012 <- read_csv("~/Final paper/data/raw_data/raw_data_2012.csv")
data_2013 <- read_csv("~/Final paper/data/raw_data/raw_data_2013.csv")
data_2014 <- read_csv("~/Final paper/data/raw_data/raw_data_2014.csv")
data_2015 <- read_csv("~/Final paper/data/raw_data/raw_data_2015.csv")
data_2016 <- read_csv("~/Final paper/data/raw_data/raw_data_2016.csv")
data_2017 <- read_csv("~/Final paper/data/raw_data/raw_data_2017.csv")
data_2018 <- read_csv("~/Final paper/data/raw_data/raw_data_2018.csv")
data_2019 <- read_csv("~/Final paper/data/raw_data/raw_data_2019.csv")

# Add column 'year' to every dataset, since we need year when combining them

data_2009 <- mutate(data_2009, year = 2009)
data_2010 <- mutate(data_2010, year = 2010)
data_2011 <- mutate(data_2011, year = 2011)
data_2012 <- mutate(data_2012, year = 2012)
data_2013 <- mutate(data_2013, year = 2013)
data_2014 <- mutate(data_2014, year = 2014)
data_2015 <- mutate(data_2015, year = 2015)
data_2016 <- mutate(data_2016, year = 2016)
data_2017 <- mutate(data_2017, year = 2017)
data_2018 <- mutate(data_2018, year = 2018)
data_2019 <- mutate(data_2019, year = 2019)

# Combine the data

all_data <- bind_rows(data_2009, data_2010, data_2011, data_2012, data_2013,
                      data_2014, data_2015, data_2016, data_2017, data_2018, data_2019)

# Create data frame that has counts for policy area in a year

policy_area_counts <- all_data %>%
  group_by(year, policyarea) %>%
  summarise(count = n())

# Create grouped barplot with stacked bars
ggplot(policy_area_counts, aes(x = factor(year), y = count, fill = factor(policyarea))) +
  geom_bar(stat = "identity", position = "stack") +
  labs(title = "Frequency of Policy Areas Across Years",
       x = "Year",
       y = "Frequency",
       fill = "Policy Area") +
  theme_minimal() +
  scale_y_continuous(labels = comma)
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

Talk way more about it.

@@

We use a negative binomial regression model

>>>>

# Read the CSV file
all_data <- read_csv("/Users/Samarthsumitrajani/Final paper/data/raw_data/raw_data.csv")

# Convert character date column to Date format
all_data$date <- as.Date(all_data$date, format = "%m/%d/%Y")

# Create data frame that has counts for policy area in a year
policy_area_counts <- all_data %>%
  mutate(year = format(date, "%Y")) %>%
  group_by(year, policyarea) %>%
  summarise(count = n())

# Filter out NA values from the policy_area_counts dataset
filtered_data <- policy_area_counts %>%
  drop_na()

# Create grouped barplot with stacked bars
ggplot(filtered_data, aes(x = factor(year), y = count, fill = factor(policyarea))) +
  geom_bar(stat = "identity", position = "stack") +
  labs(title = "Frequency of Policy Areas Across Years",
       x = "Year",
       y = "Frequency",
       fill = "Policy Area") +
  theme_minimal() +
  scale_y_continuous(labels = scales::comma)
```

@@

We use a linear logistic regression model in order to estimate how each individual party
